\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\color{text-grey}

\titleformat{\section}{
  \bfseries\raggedright\large
}{}{0em}{}[\color{light-grey}\titlerule]

%-------------------------
% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}
\newcommand{\resumeLinks}[1]{
  {\small \textcolor{dark-grey}{#1}}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{#3} & {\small #4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand{\arraystretch}{1.1}


%=========================
\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge Himesh Dua} \\ \vspace{6pt}

    \faPhone*~+92~325~7555131 \quad
    \faEnvelope~\href{mailto:himeshdua22@gmail.com}{himeshdua22@gmail.com} \quad
    \faEnvelopeOpen~\href{mailto:himesh2407b@aptechgdn.net}{himesh2407b@aptechgdn.net} \quad
    \faGlobe~\href{https://himeshdua.vercel.app}{himeshdua.vercel.app} \quad
    \faGithub~\href{https://github.com/himeshdua}{github.com/himeshdua} \quad
    \faLinkedin~\href{https://linkedin.com/in/himeshdua}{linkedin.com/in/himeshdua}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\small{
React-focused Frontend Engineer with strong expertise in \textbf{Next.js (App Router)}, TypeScript, and modern UI systems. Experienced in building \textbf{high-performance, production-grade web applications} with SSR, caching, and scalable frontend architectures. Comfortable collaborating across the stack when needed.
}

%-----------SKILLS-----------
\section{TECHNICAL SKILLS}
\small{
\textbf{Frontend:} Next.js, React, TypeScript, Tailwind CSS, Shadcn UI, Flutter \\
\textbf{State \& Data:} Zustand, React Server Components, Caching Strategies, IndexedDB, Prisma ORM \\
\textbf{Backend:} Node.js, Laravel, Inertia.js, Firebase Auth, Clerk Auth, ASP DOTNET \\
\textbf{Databases:} PostgreSQL, MySQL, Supabase, Firebase \\
\textbf{Tools \& Platforms:} Vercel, Git, GitHub, Docker, Postman, Dart
}


%-----------PROJECTS-----------
\section{PROJECTS}

\resumeSubHeadingListStart

% LIBREBOOKS
\resumeSubheading
  {LibreBooks}
  {2025 -- 2026}
  {Next.js (App Router) $\cdot$ Supabase $\cdot$ Zustand $\cdot$ IndexedDB $\cdot$ OAuth}
  {\resumeLinks{
    \href{https://librebooks.vercel.app}{librebooks.vercel.app}
    \quad
    \href{https://github.com/himeshdua/librebooks}{GitHub}
  }}
\resumeItemListStart
\resumeItem{Architected a \textbf{production-grade digital library} using Next.js App Router with server components and route-based data fetching, delivering fast page loads across a 12,000+ book catalog.}
\resumeItem{Ingested and indexed \textbf{12,000+ public-domain books} from the GutenDex API, designing scalable pagination and multi-dimensional filtering by language, genre, and author.}
\resumeItem{Built a \textbf{personalized recommendation engine} surfacing books by user language and category preferences, improving content discoverability for both authenticated and guest users.}
\resumeItem{Persisted user favorites across sessions using \textbf{Zustand + IndexedDB}, enabling offline-capable interactions without server round-trips.}
\resumeItemListEnd

% DEVGRADE
\resumeSubheading
  {DevGrade}
  {2025}
  {Next.js $\cdot$ TypeScript $\cdot$ GitHub API $\cdot$ Data Visualization}
  {\resumeLinks{
    \href{https://devgrade.vercel.app}{devgrade.vercel.app}
  }}
\resumeItemListStart
  \resumeItem{Built an \textbf{automated developer assessment platform} that analyzes code quality and productivity metrics, enabling data-driven technical hiring decisions.}
  \resumeItem{Designed \textbf{analytical dashboards} visualizing GitHub activity --- commit frequency, PR velocity, and repository health --- for structured, objective candidate evaluation.}
  \resumeItem{Automated candidate screening workflows via the \textbf{GitHub API}, reducing manual evaluation effort and standardizing assessment criteria across hiring pipelines.}
\resumeItemListEnd

% NETNEST
\resumeSubheading
  {NetNest}
  {2025}
  {Laravel 12 $\cdot$ Inertia.js $\cdot$ React $\cdot$ MySQL}
  {\resumeLinks{
    \href{https://github.com/himeshdua/netnest}{GitHub}
  }}
\resumeItemListStart
  \resumeItem{Co-developed a \textbf{full-stack ISP management platform} showcased at \textbf{Aptech Vision 2025}, handling customer billing, service plans, and network account management.}
  \resumeItem{Engineered \textbf{role-based dashboards} with granular permission logic across admin, agent, and customer roles, backed by a normalized relational data model.}
  \resumeItem{Delivered a seamless \textbf{SPA experience} using Inertia.js to bridge Laravel and React, eliminating full-page reloads without sacrificing server-side routing or security.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
    {Aptech}{2024 -- 2027}
    {Advanced Diploma in Software Engineering}{Pakistan}
\resumeItemListStart
    \resumeItem{Focused on software architecture, databases, and modern development}
\resumeItemListEnd

\resumeSubheading
    {Board of Secondary Education Karachi}{2024}
    {Matriculation}{Pakistan}

\resumeSubHeadingListEnd

\end{document}
